CODE CHECK

### 2019-12-09 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- role of data and code, data science
- reproducible resarch
- data enclaves
- CASCAID
- ROpenSci/PyOpenSci

@@

- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!

>>>>

- role of data and code, data science
- reproducible resarch
- data enclaves
- CASCAID
- ROpenSci/PyOpenSci
- time capsules > https://twitter.com/DougBlank/status/1135904909663068165?s=09

@@

- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...
